Response to the defense feedback

### 2021-06-01 SupplementaryMaterial/Acknowledgments.tex
Updates from Overleaf

% Place acknowledgments below.
I am tremendously fortunate to have been advised by Dr. Dinghao Wu.  I thank Dinghao for inviting me to EPFL on his sabbatical. A large portion of the research presented in the dissertation was finished when I worked in Switzerland. The knowledge and skills I learned from him will also help me make progress in my future career. I also thank him for treating me as an independent researcher during my Ph.D. study. I had a very hard time during the pandemic. Without his encouragement and support, I could not have finished the program.

Besides my advisor, I also thank my committee members, Dr. Peng Liu, Dr. Sencun Zhu, Dr. Benjamin Hanrahan, and Dr. James Larus, for their time, reviewing my dissertation. Without the strong encouragement from Dr. Peng Liu's former students in 2015, I would not have applied for Penn State.

>>>>

% Place acknowledgments below.
I am tremendously fortunate to have been advised by Dr. Dinghao Wu.  I thank Dinghao for inviting me to EPFL on his sabbatical. A large portion of the research presented in the dissertation was finished when I worked in Switzerland. I also thank him for treating me as an independent researcher during my Ph.D. study. I had a very hard time during the pandemic. Without his encouragement and support, I could not have finished the program.

Besides my advisor, I thank my committee members, Dr. Peng Liu, Dr. Sencun Zhu, Dr. Benjamin Hanrahan, and Dr. James Larus, for their time, reviewing my dissertation.
